Full title of the paper (Capitalized)

### 2022-03-06 Paper_Draft1/Draft1.Rmd
adding to bibliography section

# Bibliography
Citing book reference @gujer_systems_2008
Citing reference with parentheses [@leutnant_stormwater_2016]

@hardin2015data advocated for more data science in statistics curricula.

>>>>

# Bibliography

@angwin2016machine
@hardin2015data
@larson2016we
@gebru2021datasheets
@noauthor_aif360datasetscompasdataset_2018
@noauthor_propublicacompas-analysis_2022
@larson2016technical
@bao2021s
@barocas2017fairness
@knight2020automated
@kypraiou_what_2021
@equivant_response_2018
@baumer2017texts
@james2013introduction
@noauthor_ai_nodate
@noauthor_trusted-ai_360
@vartan_1st_2022
@noauthor_womenthetable_nodate
